analysis

### 2022-10-24 r-analysis/analysis.Rmd
exported  code to plot and datasource files

```{r overview statistics: emissions per capita development 1970:2020}
data_countries <- data_ghg %>% 
  group_by(ISO,country,year) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE))

#data_countries <- left_join(data_countries,data_wdi %>%
#                              select(-country),by=c("ISO","year"))

data_countries <- data_countries %>% 
  mutate(GHG_pc=GHG/pop)

>>>>

```{r overview statistics: emissions per capita development 1970:2020}
YEAR = 2019

source("r-analysis/china_and_regions.R", local = TRUE, print.eval = TRUE)
source("r-plots/china_and_regions.R", local = TRUE, print.eval = TRUE)
